rowing: analysis of sculls in the 2016 Olympics

### 2021-02-01 inst/rowing.Rmd
race() and tidyup

f <- function(filename){
  o <- strsplit(readLines(filename)," ")

  rowers <- sort(unique(unlist(o)))
  H <- hyper2(list(),0,pnames=rowers)

  for(v in o){
      v <- rev(v)
      for(i in seq_along(v)){
          H[v[i]] %<>% inc           # H[v[i]] %<>% `+`(1)
          H[v[seq_len(i)]] %<>% dec  # H[v[seq_len(i)]] %<>% `-`(1)
      }
  }
  return(H)
}

>>>>

f <- function(filename){
  o <- strsplit(readLines(filename)," ")
  H <- hyper2()
  for(v in o){H <- H + race(v)}
  return(H)
}
